### 2023-09-11 Notes/model_assumptions.tex
Added non-linear simulation for estimation comparison.

These estimated variances are almost exactly in line with the estimated
standard deviations from the simulation study. With values of $n = 1000$,
$\sigma_{11} = 1$, $\sigma_{22} = 1$, $\sigma_{12} = 0.5$, $\theta_2 = 5$,
$\pi_{11} = 0.4$, $\pi_{10} = 0.2$, $\pi_{01} = 0.2$, and $\pi_{00} = 0.2$
the standard deviations from the previous calculations and from the Monte Carlo
simulation are listed in the Table~\ref{tab:calmc}:

@@

@@

\begin{itemize}
  \item[1.] Since we have a way to estimate the variance, the goal is still 
    to find the optimal $a$ and $b$ for Equation~\ref{eq:propclass}.
\end{itemize}

>>>>

These estimated variances are almost exactly in line with the estimated
standard deviations from the simulation study. With values of $n = 1000$,
$\sigma_{11} = 1$, $\sigma_{22} = 1$, $\sigma_{12} = 0.5$, $\theta_2 = 5$,
$\pi_{11} = 0.4$, $\pi_{10} = 0.2$, $\pi_{01} = 0.2$, and $\pi_{00} = 0.2$
the standard deviations from the previous calculations and from the Monte Carlo
simulation are listed in Table~2:
%Table~\ref{tab:calmc}:

@@

\newpage
  \quad
\newpage

\section*{Non-linear Estimation}

\begin{itemize}
  \item While we have previously shown that in the case of the linear 
    estimator, that the weighted least squares (WLS) estimator is superior 
    to the proposed estimator. However, we also want to see if this holds 
    for a non-linear function. Consider the estimating equation $g(X, Y_1, Y_2)
     = Y_1^2 Y_2$. Using the same setup as the previous simulation, we have the
     same definitions of $X$, $Y$, $n$, $\pi$, and $B$.

     For the definition of each estimator we have the following algorithms:

     \begin{itemize}
      \item Oracle: This computes the average value of $Y_1^2Y_2$ in all 
        observations (even when $Y_1$ or $Y_2$ is not supposed to be observed).
        \[\hat \theta = n^{-1} \sum_{i = 1}^n y_{1i}^2y_{2i}.\]

      \item OracleX: This computes the average value of $Y_1^2 (Y_2 - X)$ in 
        all observations (even when $Y_1$ or $Y_2$ is not supposed to be observed.)
        \[\hat \theta = n^{-1} \sum_{i = 1}^n y_{1i}^2(y_{2i} - x_i).\]

      \item CC: This computes the average value of $Y_1^2Y_2$ in all
        observations in which $Y_1$ and $Y_2$ are observed.
        \[\hat \theta = \frac{\sum_{i = 1}^n \delta_{1i}\delta_{2i} y_{1i}^2y_{2i}}
        {\sum_{i = 1}^n \delta_{1i}\delta_{2i}}.\]

      \item Proposed: This is the proposed estimator from Equation~\ref{eq:prop}.
        Note that since,

        \begin{align*}
          Y_1^2 Y_2 &= (x + e_1)^2 (\theta_2 + x + e_2) \\ 
                    &= x^3 + x^2 (\theta_2 + 2 e_1 + e_2) 
                    + x(2\theta_2 e_1 + 2 e_1 e_2 + e_1^2) + e_1^2 \theta_2 
                    + e_1^2 e_2
        \end{align*}

        for the conditional expectations, we have
        \begin{align*}
          E[Y_1^2 Y_2 \mid X] &= x^3 + x^2 \theta_2 + x(2\sigma_{12} + 1) + \theta_2\\
          E[Y_1^2 Y_2 \mid X, Y_1] &= Y_1^2 (x + \theta_2) \text{ and }\\
          E[Y_1^2 Y_2 \mid X, Y_2] &= (x^2 + 1) Y_2.
        \end{align*}

      \item WLS: To derive the WLS estimator we can view the sample as 
        consisting of four independent parts: $A_{11}, A_{10}, A_{01}$, and 
        $A_{00}$, where $A_{ij}$ indicates the missingness levels of $Y_1$ (if 
        i = 0) or $Y_2$ (if $j = 0$). We know that the correctly specified
        regression model for $g$ in each of these segments is the following:

        \begin{align*}
          A_{11}&: Y_1^2 Y_2 \\
          A_{10}&: Y_1^2  (x + \theta_2) \\
          A_{01}&: (x^2 + 1) Y_2\\
          A_{00}&: x^3 + x^2 \theta_2 + x(2\sigma_{12} + 1) + \theta_2
        \end{align*}

        The estimator is then to estimate $\theta_2$ using Equation~\ref{eq:wls}.
        Then, we can plug in the estimated value of $\theta_2$ into the previous 
        equations to get estimates of $g$. The overall estimate is the estimated 
        variance weighted average of the mean estimate from each segment.

      \item WLSTT: Since the previous estimator is biased, we use the same
        estimation procedure with the true value of $\theta_2$ to the estimator 
        $\hat \theta_{WLSTT}$.
     \end{itemize}

     \begin{table}[!ht]
       \caption{True g is 10. $\Cov(e_1, e_2) = 0.5$}
       \centering
       \begin{tabular}[t]{lrrrr}
         \toprule
         Algorithm & Bias & SD & Tstat & Pval\\
         \midrule
         Oracle & 0.007 & 0.529 & 0.741 & 0.229\\
         Oraclex & 0.004 & 0.475 & 0.510 & 0.305\\
         CC & 0.023 & 0.824 & 1.518 & 0.065\\
         WLS & -0.131 & 0.387 & -18.504 & 0.000\\
         WLSTT & -0.132 & 0.380 & -19.007 & 0.000\\
         Prop & 0.011 & 0.625 & 0.952 & 0.171\\
         \bottomrule
       \end{tabular}
     \end{table}

     In this scenario, the WLS estimator is biased. Other than the oracle 
     estimators, the proposed estimator is the best unbiased estimator.

@@

\begin{itemize}
  \item I am slightly unclear about how to proceed. The proposed estimator 
    seemed to work quite well for the non-linear experiment. However, it was 
    easily out-performed by the WLS estimator in the linear case. The WLS 
    estimator is a relatively intuitive estimator that is optimal in that 
    situation. However, it seems to have worse performance in the non-linear 
    case.
\end{itemize}
